---
title: "Opinionated tutorial demonstrating R reproducible workflow using workflowR."
output:
  xaringan::moon_reader:
    css: ["default","my-theme.css"]
---

# Opinion # 1 - R is the best
  * Code based research output
  * no random mouse clicking
  * open source

  * but dense

---

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}

library(kableExtra)
library(tidyverse, warn.conflicts=FALSE, verbose=FALSE, quietly=TRUE)

```

# Example Chart

```{r, warning=FALSE}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
```
---


# Example Chart (#2)

```{r, warning=FALSE}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color=class))
```
---

# Opinion # 2 - Tidyverse 'dialect' of R
  * R has 3 different code styles;  \$, formula, and tidyverse
    - [ see comparision here ](https://github.com/rstudio/cheatsheets/raw/master/syntax.pdf)  
  * tidyverse is easy to read, write and *maintain*

---

# Tidyverse example
```{r, results='asis', warning=FALSE}
  mpg %>%
    filter( cyl < 8 ) %>%
    group_by( class ) %>%
    summarise( mean( hwy )) %>%
    kable()

```
---
# Opinion # 3 - Workflowr
  * [ Workflowr Presentation from UseR 2018 conference ](2018-07-11-user.pdf) 

---

# Resources
  * [ Workflowr Presentation from UseR 2018 conference ](2018-07-11-user.pdf) 
  * [Rstudio installation](https://www.rstudio.com/products/rstudio/download/)
  * [R installation](https://cran.rstudio.com/)
  * [R for data science book](http://r4ds.had.co.nz/)
    - Tidyverse book with exercises
  * [Markdown documentation](https://daringfireball.net/projects/markdown/syntax)
  * [Markdown quick reference](https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet)
  * [RMarkdown cheatsheet](https://github.com/rstudio/cheatsheets/raw/master/rmarkdown-2.0.pdf)
  * [Data Transformation cheatsheet](https://github.com/rstudio/cheatsheets/raw/master/data-transformation.pdf)
  * [Data visualisation cheatsheet](https://github.com/rstudio/cheatsheets/raw/master/data-visualization-2.1.pdf)
